Classless Java

### 2015-11-17 paper/sections/Translation.tex
Typo.
Comments.
Text for theorem.

To understand this theorem statement, we need to understand that there are three kind of guarantees that we can offer
\marco{should we repeat the 3 points in the email?}\\

@@

\noindent\textbf{LEMMA 1. }
If $\II_0$ satisfies $\dom(\C_0)=\dom(\C_1)\cup\ldots\cup\dom(\C_n)\cup\dom(\methods)$, then $[\![\II_0]\!]$ satisfies $\dom'(\C_0)=\dom(\C_1)\cup\ldots\cup\dom(\C_n)\cup\dom(\methods)\cup\dom(\methods')$.\\

>>>>

\haoyuan{In theorem: $I_0$ is valid and $\QM{of}\notin\dom{I_0}$. To prove the theorem we need an extra lemma: if the translation is well defined, then $[\![\II_0]\!]$ is well formed.}

To understand this theorem statement, we need to understand that there are three kind of guarantees that we can offer for safety:
\begin{itemize}
\item \textit{Self coherence}: the generated code itself is well-formed; there are no type errors.
\item \textit{Client coherence}: the client code doesn't fail if it was not failing before code generation.
\item \textit{Heir coherence}: the heirs are safe. 
\end{itemize}
The first two levels of safety are essential to our lightweight framework, nevertheless, the third one is not needed. In Java it implies not touching the annotated interface, and surely an alternative approach is to create a new interface and generate what we need. But since we are using Lombok for the translation, the transformation is applied to the annotated interface itself. But heir coherence is indeed an issue. See below how this is affected by our approach:

\begin{lstlisting}
interface A { int x(); A withX(int x); }
@Mixin interface B extends A {}
interface C extends B { A withX(int x); }
\end{lstlisting}

Here is the client code for our example. With interface \Q@B@ annotated with \mixin, by the translation rule, it will generate a method ``\Q@B withX(int x);@'' inside, as an automatic return type refinement. But in that case, interface \Q@C@ doesn't type check.

Now we go back and read the statement of our theorem again. It illustrates that a program with the translation of \mixin applied still type checks if it did, except for the subtypes of the annotated interface (type safety of them is not guaranteed).

\haoyuan{Text needs improving.}

@@

\noindent\textbf{LEMMA 1. }
Assume that
\begin{align*}
\II_0\ &=\ \mixinAnn\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC \methods\ \cC\\
[\![\II_0]\!]\ &=\ \emptyset\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC \methods\ \methods' \cC
\end{align*}
If $\II_0$ satisfies $\dom(\C_0)=\dom(\C_1)\cup\ldots\cup\dom(\C_n)\cup\dom(\methods)$, then $[\![\II_0]\!]$ satisfies $\dom([\![\II_0]\!])=\dom(\C_1)\cup\ldots\cup\dom(\C_n)\cup\dom(\methods)\cup\dom(\methods')$.\\
